Bayesian Learning of Degenerate Linear~Gaussian~State~Space~Models using~Markov~Chain~Monte~Carlo

### 2015-09-22 notes/paper-degenerate-linear-systems.tex
Additional minor edits.

A further factorisation will also be useful, which we will refer to as the Givens decomposition (on account of its method of computation). For the rank-$\rk$ positive semi-definite covariance matrix $\lgtp$,
%
\begin{IEEEeqnarray}{rCl}
 \lgtv &=& \tvrot \tvfull \tvrot\tr %&=& \begin{bmatrix}\tvrot & \tvrotorth\end{bmatrix} \begin{bmatrix}\tvfull & \zmat \\ \zmat & \zmat\end{bmatrix} \begin{bmatrix}\tvrot\tr \\ \tvrotorth\tr\end{bmatrix} \label{eq:givens_decomposition}
\end{IEEEeqnarray}
%
where,
%
$\tvfull$ is a $\rk\times\rk$ positive definite matrix and $\tvrot$ is a $\lsd\times\rk$ matrix of orthonormal vectors subject to certain constraints. The transformation from $\lgtv$ to $\{\tvfull, \tvrot\}$ is also bijective. See appendix~\ref{app:givens-factorisation} for details.

>>>>

A further factorisation will also be useful, which we will refer to as the Givens decomposition (on account of its method of computation). For the rank-$\rk$ positive semi-definite covariance matrix $\lgtp$,
%
\begin{IEEEeqnarray}{rCl}
 \lgtv &=& \tvrot \tvfull \tvrot\tr \label{eq:givens_decomposition} %&=& \begin{bmatrix}\tvrot & \tvrotorth\end{bmatrix} \begin{bmatrix}\tvfull & \zmat \\ \zmat & \zmat\end{bmatrix} \begin{bmatrix}\tvrot\tr \\ \tvrotorth\tr\end{bmatrix}
\end{IEEEeqnarray}
%
where,
%
$\tvfull$ is a $\rk\times\rk$ positive definite matrix and $\tvrot$ is a $\lsd\times\rk$ matrix of orthonormal vectors subject to certain constraints. The transformation from $\lgtv$ to $\{\tvfull, \tvrot\}$ is also bijective. See appendix~\ref{app:givens-factorisation} for details.
